---
title: "CSEd-Refresh: Computing Courses in California"
output: 
  flexdashboard::flex_dashboard:
    theme: default
    orientation: columns
    vertical_layout: fill
    social: menu
    source_code: embed

---

```{r setup, include=FALSE}
library(shiny)
library(flexdashboard)
library(leaflet)
library(dplyr)
library(DT)
library(readr)

courses <- read_csv("Courses.csv")
topoData <- readLines("caCountiesTopo.json") %>% paste(collapse = "\n")
popup_info <- paste("<b>School:</b>", courses$schoolname, "<br>", 
                    "<b>District</b>:", courses$districtname, "<br>",
                    "<b>Course</b>:", courses$coursetitle, "<br>")

```

Sidebar {.sidebar}
=======================================================================
Use the __Visualization__ tab to explore the various computing courses offered throughout California for academic year 2014-2015. All of the courses visualized on the map are listed on the control panel on the right. You can use the radio buttons to show--or hide--the courses you are most interested in. The full course description for each of the computing courses listed here are available on the __Course Descriptions__ page. 

Click the __Data Explorer__ tab to examine how locally-weighted estimates of neighborhood diversity by distance from the urban core has varied between the 1990, 2000, and 2010 Censuses, and view maps of these shifts over time. To learn more about the project, click the __About__ tab.

Download CDE's courses taught data [_here_](http://www.cde.ca.gov/ds/sd/df/filesassign.asp).

Application author: [Debra Richardson & Vinh Luong](http://www.ics.uci.edu)
[Expanding Computing Educaton Pathways--California](http://www.uci.edu)

```{r}

```


Visualization
=======================================================================

```{r}

m <- leaflet() %>%
  
  addProviderTiles("CartoDB.Positron") %>%
  setView(lng = -117.946320, lat = 36.046033, zoom = 7) %>%
  addTopoJSON(topoData, weight = 1, color = "#444444", fill = FALSE) %>%
  
  #Markers for 2451 Computer Programming
  addCircles(data = dplyr::filter(courses,coursecode == "2451"),~lng, ~lat, 
    popup = popup_info, weight = 3, radius = 60,
    color = "#a6cee3", stroke = TRUE, fillOpacity = 0.8,
    group = "2451 Computer Programming") %>%
  
  #Markers for 2453 Computer Science
  addCircles(data = dplyr::filter(courses,coursecode == "2453"),~lng, ~lat, 
    popup = popup_info, weight = 3, radius = 60,
    color = "#1f78b4", stroke = TRUE, fillOpacity = 0.8,
    group = "2453 Computer Science") %>%
  
  #Markers for 2458 Other Computer Education
  addCircles(data = dplyr::filter(courses,coursecode == "2458"),~lng, ~lat, 
    popup = popup_info, weight = 3, radius = 60,
    color = "#b2df8a", stroke = TRUE, fillOpacity = 0.8,
    group = "2458 Other Computer Education") %>%
  
  #Markers for 2465 IB Computer Science
  addCircles(data = dplyr::filter(courses,coursecode == "2465"),~lng, ~lat, 
    popup = popup_info, weight = 3, radius = 60,
    color = "#33a02c", stroke = TRUE, fillOpacity = 0.8,
    group = "2465 IB Computer Science") %>%
  
 #Markers for 2466 IB Information Technology in a Global Society
  addCircles(data = dplyr::filter(courses,coursecode == "2466"),~lng, ~lat, 
    popup = popup_info, weight = 3, radius = 60,
    color = "#fb9a99", stroke = TRUE, fillOpacity = 0.8,
    group = "2466 IB Information Technology in a Global Society") %>%
  
  #Markers for 2470 AP Computer Science A
  addCircles(data = dplyr::filter(courses,coursecode == "2470"),~lng, ~lat, 
    popup = popup_info, weight = 3, radius = 60,
    color = "#e31a1c", stroke = TRUE, fillOpacity = 0.8,
    group = "2470 AP Computer Science A") %>%
  
  #Markers for 2471 AP Computer Science AB
  addCircles(data = dplyr::filter(courses,coursecode == "2471"),~lng, ~lat, 
    popup = popup_info, weight = 3, radius = 60,
    color = "#fdbf6f", stroke = TRUE, fillOpacity = 0.8,
    group = "2471 AP Computer Science AB") %>%
  
  #Markers for 2479 MYP Computer Technology
  addCircles(data = dplyr::filter(courses,coursecode == "2479"),~lng, ~lat, 
    popup = popup_info, weight = 3, radius = 60,
    color = "#ff7f00", stroke = TRUE, fillOpacity = 0.8,
    group = "2479 MYP Computer Technology") %>%
  
  #Markers for 4601 Computer Operations / Computer Science
  addCircles(data = dplyr::filter(courses,coursecode == "4601"),~lng, ~lat, 
    popup = popup_info, weight = 3, radius = 60,
    color = "#cab2d6", stroke = TRUE, fillOpacity = 0.8,
    group = "4601 Computer Operations/Computer Science") %>%
  
  #Markers for 4616 Computer Programming and Game Design
  addCircles(data = dplyr::filter(courses,coursecode == "4616"),~lng, ~lat, 
    popup = popup_info, weight = 3, radius = 60,
    color = "#6a3d9a", stroke = TRUE, fillOpacity = 0.8,
    group = "4616 Computer Programming and Game Design") %>%
  
  #Markers for 4619 Computer Programming for Solving Applied Problems
  addCircles(data = dplyr::filter(courses,coursecode == "4619"),~lng, ~lat, 
    popup = popup_info, weight = 3, radius = 60,
    color = "#ffff99", stroke = TRUE, fillOpacity = 0.8,
    group = "4619 Computer Programming for Solving Applied Problems") %>%
  
  #Markers for 4634 Exploring Computer Science
  addCircles(data = dplyr::filter(courses,coursecode == "4619"),~lng, ~lat, 
    popup = popup_info, weight = 3, radius = 60,
    color = "#b15928", stroke = TRUE, fillOpacity = 0.8,
    group = "4634 Exploring Computer Science") %>%
  
  #Markers for 4647 Robotics Technologies
  addCircles(data = dplyr::filter(courses,coursecode == "4647"),~lng, ~lat, 
    popup = popup_info, weight = 3, radius = 60,
    color = "#01665e", stroke = TRUE, fillOpacity = 0.8,
    group = "4647 Robotics Technologies") %>%
     
    addLayersControl(
      overlayGroups = c("2451 Computer Programming", "2453 Computer Science",
                        "2458 Other Computer Education", "2465 IB Computer Science",
                        "2466 IB Information Technology in Global Society", 
                        "2470 AP Computer Science A", "2471 AP Computer Science AB", 
                        "2479 MYP Computer Technology",
                        "4601 Computer Operations/Computer Science", 
                        "4616 Computer Programming and Game Design",
                        "4619 Computer Programming for Solving Applied Problems",
                        "4634 Exploring Computer Science", "4647 Robotics Technologies"),
      options = layersControlOptions(collapsed = FALSE)
    )
m

```

Data Explorer
=======================================================================

```{r}

datatable(dplyr::select(courses,districtcode, schoolcode, countyname,
                        districtname, schoolname, coursecode, coursetitle),
  colnames = c('District Code', 'School Code','County','District',
               'School','Course Code','Course Title'),
  extensions = c('Buttons', 'FixedHeader'), 
  rownames = FALSE,
  options = list(dom = 'Bfrtip',
    buttons = list('copy', 'print', 
      list(extend = 'collection', 
      buttons = c('csv', 'excel', 'pdf'),
      text = 'Download'),
      I('colvis')),
    pageLength = 100,
    fixedHeader = TRUE, 
    searchHighlight = TRUE)
)
```

Course Descriptions
=======================================================================

###General Education


```{r}

```


